---
title: "RT3"
author: "Darianys Tayrí Hernández Rivera"
date: "2026-10-01, 9:00pm"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
data("trees")
head(trees)
```

Q1. Create a histogram showing the distribution of Girth.
Q1. Cree un histograma que muestre la distribución de Girth.
```{r}
girth_hist <- ggplot(data = trees, mapping = aes(x = Girth)) +
  geom_histogram(fill = "pink", bins=8, alpha = 0.7) +
  geom_text( stat = "bin", bins = 8, aes(label = after_stat(count)), vjust = -0.5) +
  ggtitle("Distribution of Girth") +
  theme_classic()
girth_hist
```
<br>
Q2. Create a histogram showing the distribution of Volume.
Q2. Cree un histograma que muestre la distribución de Volume.
```{r}
vol_hist <- ggplot(data = trees, mapping = aes(x = Volume)) +
  geom_histogram(fill = "blue",bins= 6, alpha = 0.4) +
  ggtitle("Distribution of Volume") + 
  scale_x_continuous(breaks = seq(0, 80, by = 10)) + 
  scale_y_continuous(breaks = seq(0, 20, by = 2)) +
  theme_test()
vol_hist
```
<br>
Q3. Create a scatterplot showing the relationship between Girth and Volume.
Q3. Cree un gráfico de dispersión que muestre la relación entre Girth y Volume.
```{r, message= FALSE}
girth_vol_scatterplot <- ggplot(data = trees, aes(x = Girth, y = Volume)) + geom_point(color= "magenta", size= 3, shape= 17)+
  geom_smooth(method = "lm", se = FALSE, color = "pink") +
  ggtitle("Relationship Between Girth and Volume") +
  theme_light()
girth_vol_scatterplot
```
<br>
Q4. Use the Shapiro–Wilk test to assess whether Volume is normally distributed. Report the p-value and state whether the data are normally distributed.
Q4. Utilice la prueba de Shapiro–Wilk para evaluar si Volume tiene una distribución normal. Reporte el valor de p e indique si los datos tienen una distribución normal.
```{r}
vol_test <- shapiro.test(trees$Volume)
vol_test
# The reported p-value is 0.0036. Since p-value < 0.05 the Volume is not normally distributed. Null hypothesis of normality is rejected.
```
<br>
Q5. Repeat the Shapiro–Wilk test for Girth. Report the p-value and state whether Girth is normally distributed.
Q5. Repita la prueba de Shapiro–Wilk para Girth. Reporte el valor de p e indique si los datos tienen una distribución normal.
```{r}
girth_test <- shapiro.test(trees$Girth)
girth_test
# The reported p-value is 0.089. Since p-value > 0.05 it failed to reject null hypothesis of normality.
```



